{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-11 paper/paper.tex
renamed discussion section
corrected a sentence in the motivation
added structure of section 'discussion'

The idea of Barthe et. al. was to close this channel by compiling
type information into the byte-code, which cause the scheduler to
treat the secure parts in a different way. Since many mobile
platforms already use some byte-code (e.g. Android a modification
of the JVM byte-code).

\section{Introduction to research area}
\label{sec:introduction}
\section{Discussion of a solution}
\label{sec:discussion}
\section{Related Work}
\label{sec:relatedwork}
\section{Conclusion \& Outlook}
\label{sec:conclusion}

>>>>

The idea of Barthe et. al. was to close this channel by compiling
type information into the byte-code, which cause the scheduler to
treat the secure parts in a different way. The fact that many mobile
platforms already use some byte-code (e.g. Android a modification
of the JVM byte-code) may have been a reason for the decision to use
type-annotated byte-code.

\section{Introduction to research area}
\label{sec:introduction}
\section{Discussion of the paper}
\label{sec:discussion}
\subsection{Syntax and Semantics of multithreaded programs}
\label{sec:syntaxsemantics}
\subsection{Type system}
\label{sec:typesystem}
\subsection{Soundness}
\label{sec:soundness}
\subsection{Instantiation}
\label{sec:instantiation}

\section{Related Work}
\label{sec:relatedwork}
\section{Conclusion \& Outlook}
\label{sec:conclusion}
